\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-13 paper/sp.tex
cite

We take the \apogee\ (\citealt{aapogee, wapogee, apogee}) spectral data
from \sdssiv\ (\citealt{sdssiv}) \acronym{DR14} (\citealt{dr14}).
Because we want to make a purely linear model, which has very little capacity,
we restrict our consideration to a small region in stellar parameter space.
We cut the \apogee\ data down to the range $0<\logg<2.2$, which isolates
stars that are more luminous than the red clump.
The \apogee\ pipeline $\logg$ values (which we use) have uncertainties but
this cut leads to a clean sample of luminous red giants, and it is a cut
that is only on spectral properties of the stars (and not photometry nor astrometry).

>>>>

We take the \apogee\ (\citealt{aapogee, wapogee, apogee}) spectral data
from \sdssiv\ (\citealt{sdssiv}) \acronym{DR14} (\citealt{dr14}).
Because we want to make a purely linear model, which has very little capacity,
we restrict our consideration to a small region in stellar parameter space.
We cut the \apogee\ data down to the range $0<\logg<2.2$, which isolates
stars that are more luminous than the red clump.
The \apogee\ pipeline (\citealt{aspcap})
values of surface gravity $\logg$ (which we use) have uncertainties but
this cut leads to a clean sample of luminous red giants, and it is a cut
that is only on spectral properties of the stars (and not photometry nor astrometry).
